The semantic drift of quotations in blogspace: a case study in short-term cultural evolution

### 2017-02-03 brains-conclusion.tex
formatting: clean up source tex from irrelevant comments
formatting: fix all references

% A few more unredacted ideas:
% More broadly with Sperber:
%  - you can have a simplistic interpretation and expect simple convergence, or you can look for attraction on different dimensions, which is a richer (and more useful) interpretation.
%  - note also that it can apply to long term or short term evolution.
%  - What we see is not clear w.r.t. convergence: (1) we don't observe it on our data, and (2) if there's lineage specificity there's no reason convergence should appear (on contrary). But, this is only half the story, since in reality there's also selection, i.e. not all chains go on forever, so you lose some diversity, and it changes the dynamics.
%  - finally, context is addressed with relevance in Sperber, but it's still all representational, as we did here. Others have said that it will never be enough. Ingold, Di Paolo.

@@

Let us conclude by noting that the question of short- and long-term cultural evolution, and the approaches to study them, are becoming increasingly relevant to other fields.
In biology in particular, work on evo-devo and non-genetic inheritance has accumulated evidence that is poorly accounted for by the modern synthesis of biological evolution, and is creating a demand for new or extended  approaches to joint cultural and biological evolution~\citep[see][for instance]{gilbert_eco-evo-devo:_2015}.
Such an approach has long been called upon by anthropologists like~\citet{ingold_beyond_2004,ingold_three_1999}, in line with Mauss' initial works~\citep{mauss_les_1936}, and the question is not entirely foreign to the enactive-representational debate in cognitive science.
%As regards our particular case, a most promising line of work on the evolution of language is being developed by \citet{cuffari_participatory_2014}.
The study of cultural evolution will most likely benefit greatly from the growing interactions between these disciplines.

>>>>

@@

Let us conclude by noting that the question of short- and long-term cultural evolution, and the approaches to study them, are becoming increasingly relevant to other fields.
In biology in particular, work on evo-devo and non-genetic inheritance has accumulated evidence that is poorly accounted for by the modern synthesis of biological evolution, and is creating a demand for new or extended  approaches to joint cultural and biological evolution~\citep[see][for instance]{gilbert_eco-evo-devo:_2015}.
Such an approach has long been called upon by anthropologists like~\citet{ingold_beyond_2004,ingold_complementarity_1998}, in line with Mauss' initial works~\citep{mauss_les_1936}, and the question is not entirely foreign to the enactive-representational debate in cognitive science.
The study of cultural evolution will most likely benefit greatly from the growing interactions between these disciplines.

### 2017-02-03 brains-protocol.tex
formatting: fix all references

We used a quotation data set collected by \citet{leskovec_meme-tracking_2009}, large enough to lend itself to statistical analysis.
This data set consists of the daily crawling of news stories and blog posts from around a million online sources, with an approximate publication rate of 900k texts per day, over a nine-month period of time from August 2008 to April 2009 (\citealp{leskovec_memetracker:_2009}).\footnote{
The original article~\citep{leskovec_meme-tracking_2009} does not provide further details on the source selection methodology.
}
\newtext{The authors automatically extracted quotations} from this corpus.
Each quotation is a more or less faithful excerpt of an utterance (oral or written) by the quoted person; for instance:
\begin{quote}
The Bank of England said, ``these operations are designed to address funding pressures over quarter-end.''
\end{quote}

>>>>

We used a quotation data set collected by \citet{leskovec_meme-tracking_2009}, large enough to lend itself to statistical analysis.
This data set consists of the daily crawling of news stories and blog posts from around a million online sources, with an approximate publication rate of 900k texts per day, over a nine-month period of time from August 2008 to April 2009 (\citealp{leskovec_meme-tracking_2009}).\footnote{
The original article~\citep{leskovec_meme-tracking_2009} does not provide further details on the source selection methodology.
}
\newtext{The authors automatically extracted quotations} from this corpus.
Each quotation is a more or less faithful excerpt of an utterance (oral or written) by the quoted person; for instance:
\begin{quote}
The Bank of England said, ``these operations are designed to address funding pressures over quarter-end.''
\end{quote}
